Reliable feature point matching

### 2013-08-11 text/main/ch2_background.tex
Wrote introduction

\chapter{Matching Local Image Features}

@@

\subsection{A Thought Experiment}

@@

A simple example would be to only consider matches that aren't deviating 
too much with respect to the average angle and distancen as considered 
by \cite{kim2008efficient}.  This performs well in situations where no 
camera rotation occurs between the two images, but fails when this 
assumption isn't met. Various scenarios have been proposed to improve on 
this simple assumption such as epipolar constraints 
(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
Epipolar constraint carries the assumption that the two images matched 
are related by an affine transformation. That is, that there is no 
relative movement of objects in between images and either the viewpoint 
is fixed or the image resides entirely on a plane. In practice this 
assumption largely holds true when all objects we are interested in 
matching are roughly the same distance from the camera given that 
objects don't move across images.  Pairwise constraints provide a more 
robust approach to the same problem by looking at a set of proposed 
correspondences and defining a pairwise error between any two matches 
for example based on the assumption that two neighboring correspondences 
will usually have similar angles and distances. We can then convert the 
problem to an optimization problem and return a set of correspondences 
that minimizes this error such as proposed in \cite{choi2009robust} and 
\cite{leordeanu2005spectral}.  This approach provides more robustness in 
cases where assumptions that are violated globally still hold on a local 
scale.

@@

In practice there are many situations where relying on the geometry of 
the image to filter correspondences is not possible, for example images 
without overlap, or adjacent objects in one image are that are separated 
in another. Furthermore, methods using geometric constraints all require 
an initial set of correspondences. If this set of correspondences can be 
narrowed down to the most probable correct matches, the geometric 
matching algorithm will benefit in terms of speed and accuracy.  Finally 
some use cases might require a speed that simply cannot be achieved by 
complex geometric methods.

@@

%Matching feature points
% - What applications require matching?
% - How is matching usually done
% - Segue into related work from paper

>>>>

\chapter{Matching Local Image Features}
\label{C:background}

@@

\subsection{An Ever Changing Constant World}

@@

A simple example would be to only consider matches that aren't deviating 
too much with respect to the average angle and distancen as considered 
by \cite{kim2008efficient}.  This performs well in situations where no 
camera rotation occurs between the two images, but fails when this 
assumption isn't met. Various scenarios have been proposed to improve on 
this simple assumption such as epipolar constraints 
(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral} --- 
later referred to as \emph{Spectral}).  The Epipolar constraint carries 
the assumption that the two images matched are related by an affine 
transformation.  That is, that there is no relative movement of objects 
in between images and either the viewpoint is fixed or the image resides 
entirely on a plane.  In practice this assumption largely holds true 
when all objects we are interested in matching are roughly the same 
distance from the camera given that objects don't move across images.  
Pairwise constraints provide a more robust approach to the same problem 
by looking at a set of proposed correspondences and defining a pairwise 
error between any two matches for example based on the assumption that 
two neighboring correspondences will usually have similar angles and 
distances. This approach provides more robustness in cases where 
assumptions that are violated globally still hold on a local scale.

@@

In practice there are many situations where relying on the geometry of 
the image to filter correspondences is not possible, for example images 
without overlap, or adjacent objects in one image are that are separated 
in another. In these cases the assumptions behind the geometric 
algorithms will often cause them to return incorrect matches.

In addition methods using geometric constraints all require an initial 
set of correspondences. If this set of correspondences can be narrowed 
down to the most probable correct matches, the geometric matching 
algorithm will benefit in terms of speed and accuracy.  Finally some use 
cases might require a speed that simply cannot be achieved by complex 
geometric methods.

@@

The two methods we propose in this paper are inspired by a simple but 
novel idea. If a given feature point in one image is better matched with 
other feature points from the \emph{same} image than points in the other 
image, then any matches from this feature point to points in the other 
image are considered unreliable and should be discarded.  This approach 
carries no implicit assumptions about the geometric consistency of 
matches and as such can easily be extended with other geometric 
solutions when appropriate or necessary.

Based on this idea,  we determine reliable matches as follows. 
\emph{Mirror Match (MM)} matches every feature from both images with all 
other features and filters matches based on the ratio of best to second 
best match as in \emph{SIFT}. \emph{Mirror Match with Clustering (MMC)} 
on the other hand takes the combined set of feature points from both 
images and clusters these points according to their descriptors.  If a 
resulting partition contains only feature points from one image, no 
matches are returned.  If the partition contains points from both 
images, \emph{Mirror Match} is used to find the best matches within this 
partition.  The experimental results show that both approaches generally 
outperform existing correspondence matching methods.
